### 2019-12-20 README.Rmd
updated docs

### Downloading from GitHub for development

1. Use RStudio to create a local copy of the project
    1. In RStudio, start a new Project: `File > New Project > Version Control > Git`
    1. In the “repository URL” paste: https://github.com/jlucasmckay/msBalance
    1. On OS X, you can make this under `tmp` - this is a temporary file that can be deleted later
    1. If there are files that need to be added to the remote, they can be placed in this folder or dragged / dropped into the GitHub interface.
1. Path locations that need to be read by Matlab and R can be specified in `msBalance/paths.m`.
1. Path locations might need to be modified in `msBalance/m/loadData.m`.
1. The main analysis is in `msBalance/R/msBalance.Rmd`
1. Stage changed files, commit, and push changes with the git panel.

### Navigating a mixture of Matlab and R code

1. The source files are in `.mat` format.
1. There is a mixture of matlab preprocessing code (files in `m/`) into `.csv` files that R can then read (files in `R/`).
1. A directory `csv/` is created to hold these files. The contents of this directory are not automatically loaded to GitHub.

### Running the code

1. Alter `paths.m` to point to the correct data directory.
1. Run the Matlab code to load .mat files and populate patient-level data
    * Run `m/loadData.m` to load source files and populate the `csv/` directory.
    * A future version of this could call the Matlab script from R if useful.
1. "knit" `R/msBalance.Rmd` to produce the study document.

>>>>

### What to read and edit
1. This document explains how to run the code. It is an html version of `README.Rmd` that is "knit," which you can think of as sort-of interpreted or compiled.
1. The document `R/msBalance.html` contains the output text and figures. It is the knit/interpreted version of `R/msBalance.Rmd`

### How to run the code
1. Alter `paths.m` in the main project directory to point to the correct data directory on your local machine.
1. Run the Matlab code to load .mat files and populate patient-level data
    * Run `m/loadData.m` to load source files and populate the `csv/` directory.
    * A future version of this could call the Matlab script from R if useful.
1. "knit" `R/msBalance.Rmd` to produce `R/msBalance.html`.

### Notes related to the fact that there is a mixture of Matlab and R code
1. The source files are in `.mat` format.
1. There is a mixture of matlab preprocessing code (files in `m/`) into `.csv` files that R can then read (files in `R/`).
1. A directory `csv/` is created to hold these files. The contents of this directory are not automatically loaded to GitHub.

### How to download from GitHub for development
1. Use RStudio to create a local copy of the project
    1. In RStudio, start a new Project: `File > New Project > Version Control > Git`
    1. In the “repository URL” paste: https://github.com/jlucasmckay/msBalance
    1. On OS X, you can make this under `tmp` - this is a temporary file that can be deleted later
    1. If there are files that need to be added to the remote, they can be placed in this folder or dragged / dropped into the GitHub interface.
1. Path locations that need to be read by Matlab and R can be specified in `msBalance/paths.m`.
1. Path locations might need to be modified in `msBalance/m/loadData.m`.
1. The main analysis is in `msBalance/R/msBalance.Rmd`
1. Stage changed files, commit, and push changes with the git panel.
